{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}

### 2025-07-22 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 1$. 

@@

\section{Discussion, interpolation helps but it's not enough}
    \subsection{The no error case}
    \subsection{The degenerate case}

>>>>

            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 0$. 

@@

        Obtaining the convergence results from the lemma requires a recursive relation in expectation. 
        Before we start, here are some techinical details regarding conditional expectations. 
        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some Sigma algebra. 
        The following theorem gives necessary results to derive the convergence rate of the algorithm in expectations. 
        \begin{theorem}[SNAG descent lemma in expectations]\label{thm:snag-descent-expe}

        \end{theorem}
        \begin{proof}

        \end{proof}
\section{Discussion, interpolation helps but, it's not enough}
    \subsection{The no error case}
    \subsection{The degenerate case}
